\section{Initial Problem Statement}\label{sec:initial_problem}

The problem described in the introduction, and the one that will be used
in this project as a starting point can be summarized to the following:

\begin{problemstatement}
	How can we make an application that seamlessly synchronizes audio
	playback wirelessly between multiple devices?
\end{problemstatement}

\noindent
In order to minimize the ambiguity of the initial problem statement, 
we define and explain the terms we use, in the context of this paper as follows:

\begin{description}
	\item[Application] \hfill \\
		We imagine that the solution to the problem will include a software
		application. Which kind of application will depend on what specific
		device the use case demands. \tnote{Vejleder kalder dette for generelt. Skal vi bare slette det?}
	\item[Seamlessly synchronizes]  \hfill \\
		From the initial idea generation phase we suspect
		that the delay between devices, of the audio playback will
		play a significant role in the design of the solution. Therefore we
		want to synchronize the audio to a precision that makes it feel
		seamless to the human ear.
	\item[Wirelessly]  \hfill \\
		Part of the application being seamless is also that external wires etc. are
		not required for the devices to function together.
	\item[Amplification]  \hfill \\
		We envision that a solution would involve multiple devices to seemingly 
		amplify the signal without the distortion of trying to push sound out of
		small speakers. The devices need not be the same exact hardware.
\end{description}

To get a further understanding of the problem at hand, and to
construct a final problem statement, we will first explore use
cases for such an application. 
Then analyze some existing related solutions on the market, 
and test some of them in depth. 
We do this to understand the problem, and use that knowledge
to make a final problem statments, and a list of requirements for the project. 
