%Intro 2
For social events background music often brings a desired ambiance.
Events held outside of ones home, in particular outdoor events, often lack a qualitative way to play audio.
Smartphones, while widespread lack the hardware to play audio at higher volumes, without distortion affecting the quality.
Solutions such as wireless battery powered Bluetooth speakers do exist, but are far less common to have on your person than a smartphone.
We present an application allowing a network of smartphones to play audio in sync, effectively increasing volume without affecting quality.

\bigskip \noindent
%Theory stuff : Psycho acoustics : Current Apps(target)
    %psychoacoustics -interesting application areas - use cases
    %unsaturated Play Store with dissatisfactory apps
To initiate our project we investigate the scientific field related human auditory perception, psychoacoustics, and any apps on the Play Store.
Our research into psychoacoustics reveals a useful effect, the precedence effect, which amplifies perceived audio by using multiple slightly out of sync audio sources.
We also prove the apps on the Play Store to be unsatisfactory, requiring manual trial and error efforts to achieve audible sync. 

\bigskip \noindent
%Dev Stuff : Decoder, Player, Native, Sync, Comms
To prove it possible to make an application that outperforms those on the Play Store, we implement our own application.
We use a sample app as a framework to build upon, to reduce the amount of UI we have to concern ourselves with.
Building atop this framework, we replace the Android decoder and player with our own, and implement a communications system using the Simple Network Time Protocol to achieve clock synchronization.
We utilize timestamps to communicate between devices, nullifying any communication latency effects.

\bigskip \noindent
%Test Stuff : We are BiS because our test said so
Finally we test our application, under the same circumstances as the apps on the Play Store.
The tests reveal that we have indeed succeeded, our application outperforms those on the Play Store in regard to audible synchronization.
