\subsection{Test Discussion and Conclusion}

In the tests we have tested the questions we posed for the apps in \vref{sec:sota_test}.
These are questions which determines if the apps are suitable answers for the initial problem statement, \vref{sec:initial_problem}.
The questions are in three categories: 
\begin{enumerate*}[label=(\alph*)]
    \item Offset,
    \item Consistency,
    \item Drift.
\end{enumerate*}
We will go through each of them, and try to answer them.

\subsubsection*{Offset:}
\begin{description}
    \item[Is the audio synchronized without any manual adjustment?] \hfill \\
    For both apps, the answer is \textbf{no}. 
    This can be seen in all of the tests, for example in \vref{fig:soundseeder_test} and \vref{fig:ampmedelay_test}, where the measured delay was $-70.497 ms$ and $+131.260 ms$ for SoundSeeder and AmpMe respectively.
    
    For SoundSeeder we did the additional test of using their synchronize button. 
    This test, results in \vref{fig:soundseedersyncbutton}, show that the measure delay between the two phones are different, after pressing the synchronize button, but it does not get closer to $0$. 
    Additionally the change seems arbitrary.  
    \item[Can the manual adjustment make them synchronized?] \hfill \\
    In the tests we discovered the actual adjustments the offset sliders make. 
    SoundSeeder shows milliseconds as a unit for their slider, with a granularity of $10 ms$.
    In our tests the results, \vref{fig:soundseeder_test}, is a bit less than that, $9.744 ms$ for every $10 ms$ on their slider.
    This will allow users to get within $\frac{\pm9.744 ms}{2}=\pm 4.872 ms$ of perfect synchronization.
    
    For AmpMe, which had one with an arbitrary scale, each value is measured to be $23.211 ms$ in either direction in \vref{fig:ampmedelay_test}.
    This means that one could, theoretically, always get within $\frac{\pm23.211 ms}{2}=\pm 11.6055 ms$ of perfect synchronization. 
    So the answer to the question, is \textbf{to some degree}.
\end{description}

\subsubsection*{Consistency:}
\begin{description}
    \item[Is the delay consistent between playbacks?] \hfill \\
    To test this question we played one song, tested the delay, then switched song, and tested it again, repeated five times. 
    If the delay was consistent then the delta of these values should be close to $0$, however that is not the case for either app. 

    For SoundSeeder there was a change when changing song, to such a degree that a user would have to manually adjust the synchronization again.
    For AmpMe, the change relative to the previous was very close to one step on their slider in three out of four measurements, and the last had almost no change. 
    This is interesting, as using the manual slider could be used to correct this. 

    However for both apps the delay is \textbf{not consistent} between playback.
\end{description}

\subsubsection*{Drift:}
\begin{description}
    \item[Is the synchronization stable over time?] \hfill \\
    Yet to test formally, but we expect AmpMe to be better than SoundSeeder, but none of them to be acceptable. 
\end{description}


\begin{tenote}{inline}
    I find the following pretty poor, any suggestions for improvement would be appreciated. 
\end{tenote}
In total, both of these apps attempts to answer the initial problem statement we posed, however neither of them does so in an acceptable fashion. 
Specifically the synchronization without any manual adjustment is poor. 
And if one were to manually adjust it to be somewhat close, one can only get so far.
And even then, when the song changes, this changes the offset again, and one has to start over.
