In this chapter we present certain aspects of the system design of our system, an Android application.

We firstly present the core ideas or issues, which should be solved in the design and development.
These issues function as the connection between the aforementioned requirements and future content in the design and implementation.
The purpose is to identify and highlight the sub-problems which we need to resolve in order to solve the big problem.

The primary problem we are dealing with is the ability to execute commands and play audio synchronously.
That is, we need to have a way to execute a given action at once, on all devices.
Since we cannot expect the clocks on each Android phone to be in-sync, we need to find a way of relating their clock to a master clock.

Our core idea to reach audible synchronization is to utilize a common clock for all devices.
All issued commands would then be relative to the shared clock through timestamps, each device would know their respective offsets to the shared clock and thus be able to adjust for their clock not being synchronized.
The transmission of audio and commands should be separate, such that the devices can buffer audio data to increase stability.

This proposes several problems which would have to be resolved:
\begin{itemize}
    \item How should devices be organized?
    \item How do we connect the devices?
    \item How do we give the devices a common clock?
    \item How do we transmit audio?
    \begin{itemize}
        \item Do we send the raw files to each device ahead of time?
        \item Do we send parts of files to each device, in a streaming manner?
        \item Do we need to do some pre-computation on the audio before transmitting it?
    \end{itemize}
    \item How do we transmit commands?
\end{itemize}

\bigskip\noindent
In the following part of this chapter, we will explore the architecture of the system.

